%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
%\itemsep=0in
%\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 
\newenvironment{list1}{
	\begin{list}{\ding{113}}{%
			\setlength{\itemsep}{0in}
			\setlength{\parsep}{0in} \setlength{\parskip}{0in}
			\setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
			\setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
	\begin{list}{$\bullet$}{%
			\setlength{\itemsep}{0in}
			\setlength{\parsep}{0in} \setlength{\parskip}{0in}
			\setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
			\setlength{\leftmargin}{0.2in}}}{\end{list}}


	\textbf{\sc \bf Navid Shokouhi\\\\}
	\begin{tabular}{@{}p{2.25in}p{4in}}
		%Department of Electrical Engineering & \\            
		%ECSN 4.416 & \\%{\it Fax:}    (412) 268-7828 \\         
		%The University of Texas at Dallas &  {\it Phone:}  (469) 394-6868\\
		%800 W. Campbell Rd. &  {\it E-mail:}  navid.shokouhi@utdallas.edu\\     
		%Richardson, TX 75080, USA &  {\it web:} www.linkedin.com/in/navidshokouhi\\       
		424 Dorset Rd., &    {\it Phone:} +1 (469) 394-6868\\        
		Croydon, &  {\it E-mail:}  navid.shokouhi@utdallas.edu\\     
		Melbourne, VIC 3136  &  {\it web:} www.linkedin.com/in/navidshokouhi\\         
		Australia &  
		
	\end{tabular}
	
	\line(1,0){435}
	
	
	\vspace{0mm}
	\textbf{\sc Research Interests\\\\}
	Robust speech/speaker recognition, \\
	Acoustic Modeling, Machine learning
	
	\line(1,0){435}
	
	\textbf{\sc Education\\\\}
	{\bf The University of Texas at Dallas}, \\
	%{\em Department of Statistics} 
	\vspace*{-.1in}
	\begin{list1}
		\item[] Ph.D. Candidate, EE, Fall 2011 - present \\
		Expected graduation date: December 2016
		\begin{list2}
			\vspace*{0.in}
			\item[-]Dissertation Topic:  ``Speaker Recognition and Diarization in Co-channel Speech'' \\
			{\it Addresses tangible solutions for speaker recognition \\in multi-speaker speech signals (e.g. meetings, conversations, etc.) }
			\item[-]Advisor:  Dr. John H. L. Hansen
		\end{list2}
	\end{list1}
	\vspace{3mm}
	{\bf Amirkabir University of Technology}, Tehran, Iran\\
	%{\em Department of Mathematics and Statistics} 
	\vspace*{-.1in}
	\begin{list1}
		\item[] B.Eng., Electrical Engineering
	\end{list1}
	\vspace{0mm}
	\line(1,0){435}
	
	
	\textbf{\sc Experience\\\\}
	{\bf Intern} \hfill {June 2015 - Aug 2015}\\
	  ToyTalk Inc.
	\begin{list1}
		\item[] {\it Speech engineering intern \\Built online/offline voice activity detection
			.}
		\vspace{2mm}
	\end{list1}
	
	
	
	{\bf Research Assistant} \hfill {September 2011 - Present}\\
	The University of Texas at Dallas
	
	%\vspace{-1mm}
	%{\bf Undergraduate Research} \hfill {June 2010 - August 2011}\\
	%Amirkabir University of Technology, Tehran, Iran
	%
	%\vspace{-1mm}
	%{\bf Electronics Lab Instructor} \hfill {September 2010 - December 2010}\\
	%Amirkabir University of Technology, Tehran, Iran
	%\begin{list1}
	%\item[] {\it Responsibilities included teaching, evaluation,\\ and grading junior undergraduates.}
	%\end{list1}
	\vspace{0mm}
	\line(1,0){435}
	%\vspace{-3mm}
	
	
	\vspace{0mm}
	\textbf{\sc Honors and Awards\\\\} 
	{\bf ICASSP 2013 best student paper award} \hfill {February 2013}\\
	IEEE Signal Processing Society on behalf of IBM
	
	\vspace{2mm}
	{\bf Undergraduate Honors student}\hfill {2011}\\
	Amirkabir University of Technology, Tehran, Iran \\
	Exemption from graduate school entrance exam
	
	\vspace{0mm}
	
	\vspace{0mm}
	\line(1,0){435}
	\vspace{0mm}
	
	\textbf{\sc Projects\\\\}
	{\bf 2012 NIST Speaker Recognition Evaluation} \hfill {June 2012 - October 2012}\\
	{\it Managed the fusion/calibration system for the \\UTDallas SRE submission.}\\
	
	\vspace{-1mm}
	{\bf 2014 NIST i-vector challenge} \hfill { December 2013}\\
	
	%\vspace{-5mm}
	{\bf 2016 NIST Speaker Recognition Evaluation} \hfill { October 2016}\\
	
	{\bf CRSS-SpkrDiar} \hfill { 2016}\\
	{\it Developed C++ library for end-to-end speaker diarization.}\\
	\line(1,0){435}
	
	\textbf{\sc Skills\\} 
	\begin{list2}
		\item Python, C++, MATLAB: use on a daily basis.
		\item Perl and Bash scripting: basic familiarity for text processing.
	\end{list2}
	\vspace{0mm}
	\line(1,0){435}
	
	\textbf{\sc Test Scores\\\\}
	{\bf Iranian Regional Olympiads for University Students - Electrical Eng.} \hfill {March 2010}\\
	Tehran, Iran
	\begin{list1}
	\item[] {\it Ranked 8th}
	\end{list1}
	\vspace{-0mm}
	{\bf Iranian National Olympiads for University Students - Electrical Eng.} \hfill {June 2010}\\
	Tehran, Iran
	\begin{list1}
	\vspace{-0mm}
	\item[] {\it Ranked 20th}
	\end{list1}
	\line(1,0){435}
	\vspace{0mm}
	
	\textbf{\sc Volunteer Work\\\\}
	\vspace{0mm}
	{\bf IEEE SLT Committee Newsletter} \hfill {January 2013 - 2016}\\
	News staff reporter\\
	
	{\bf SLT 2014 organizing committee - lead student volunteer} \hfill {December 2014}\\
	\vspace{0mm}
	\line(1,0){435}
	
	\textbf{\sc Publications\\}
	
	{\bf Navid Shokouhi}, John H.L. Hansen, ``Teager-Kaiser Energy Operators for Overlapped Speech Detection, '' submitted to IEEE Trans. on ASLP (accepted). \\
	
	{\bf Navid Shokouhi}, John H.L. Hansen, ``Speaker Recognition in Co-channel Speech Using Modified Probabilistic Linear Discriminant Analysis, '' JP -- (under revision).\\
	
	 John H.L. Hansen, Mahesh Kumar Nandwana, {\bf Navid Shokouhi}, ``Analysis of human scream
	and its impact on text-independent speaker verication, '' submitted to JASA (under revision).\\
	
	Yang Zheng, {\bf Navid Shokouhi}, Nicolai Thomsen, Amardeep Sathyanarayana, John H.L. Hansen, ``Towards Developing a Distraction-Reduced Hands-Off Interactive Driving Experience using Portable Smart Devices, '' SAE Technical Paper, January 2016. \\
	
	{\bf Navid Shokouhi}, Yang Zheng, Amardeep Sathyanarayana, John H.L. Hansen, ``In-Vehicle Conversation Analysis towards Improved Driver Assistance Systems,'' 7th Biennial Workshop on DSP for In-Vehicle Systems and Safety, Berkeley, CA, October 2015.\\
	
	{\bf Navid Shokouhi}, John H.L. Hansen, ``Probabilistic Linear Discriminant Analysis for Robust Speaker Identification in Co-channel Speech,'' 16th Annual Conference of the International Speech Communication Association (INTERSPEECH), Dresden, Germany, Sept. 6-10, 2015.\\
	
	{\bf Navid Shokouhi}, Ali Ziaei, Abhijeet Sangwan, John H.L. Hansen, ``Robust Overlapped Speech Detection and its Applications in Word-Count Estimation for Prof-Life-Log Data,'' IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Brisbane, Australia, April 2015. \\

	{\bf Navid Shokouhi}, Seyed Omid Sadjadi, John H.L. Hansen, ``Co-channel Speech Detection via Spectral Analysis of Frequency Modulated Sub-bands,'' 15th Annual Conference of the International Speech Communication Association (INTERSPEECH), Singapore, September 2014.\\
	
	Gang Liu, Chengzhu Yu, Abhinav Misra, {\bf Navid Shokouhi}, John H.L. Hansen , ``Investigating State-of-the-Art Speaker Verification in the Case of Unlabeled Development Data,'' Odyssey: The Speaker and Language Recognition Workshop, Finland, 2014.\\
	
	Jamal Amini, Abdoreza Sabzi Shahrebabaki, {\bf Navid Shokouhi}, Hamid Sheikhzadeh, Kamran Raahemifar, Mahdi Eslami,  ``Speech analysis/synthesis by Gaussian mixture approximation of the speech spectrum for voice conversion'' IEEE International Symposium on Signal Processing and Information Technology (ISSPIT), Greece, December 2013.\\
	
	Amardeep Sathyanarayana, {\bf Navid Shokouhi}, Seyed Omid Sadjadi, John H.L. Hansen, ``Belt Up: Investigating the impact of in-vehicular conversation on driving performance,'' Intelligent Vehicles Symposium (IV), IEEE, Australia, June 2013. \\
	
	Taufiq Hasan, Seyed Omid Sadjadi, Gang Liu, {\bf Navid Shokouhi}, Hynek Boril, John H.L. Hansen, ``CRSS systems for 2012 NIST speaker recognition evaluation,'' IEEE International Conference on Acoustics, Speech and Signal Processing, Vancouver, BC, May 2013. \\
	
	{\bf Navid Shokouhi}, Amardeep Sathyanarayana, Seyed Omid Sadjadi, John H.L. Hansen, ``Overlapped-speech detection with applications to driver assessment for in-vehicle active safety systems,'' IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Vancouver, BC, May 2013. \\
	
	{\bf Navid Shokouhi}, Amardeep Sathyanarayana, Seyed Omid Sadjadi, John H.L. Hansen, ``Analysis of In-Vehicle Speech Activity towards Driver Safety Assessment,'' 6th Biennial Workshop on DSP for In-Vehicle Systems and Safety, Seoul, South Korea, 2013.\\
	
	{\bf Navid Shokouhi} among others, ``I4U submission to NIST SRE 2012: A large-scale collaborative effort for noise-robust speaker verification,'' 14th Annual Conference of the International Speech Communication Association (INTERSPEECH), Lyon, France, August 2013.\\\\
	
	\textbf{\sc Online Articles}
	John H.L. Hansen, {\bf Navid Shokouhi}, ``Speaker Identification: Screaming, Stress and Non-Neutral Speech, is there speaker content?'' IEEE Speech and Language Technical Committee (SLTC) Newsletter, November 2013.\\
	
	Taufiq Hasan, Gang Liu, Seyed Omid Sadjadi, {\bf Navid Shokouhi}, H Bořil, A Ziaei, Abhinav Misra, KW Godin, John H.L. Hansen, ``UTD-CRSS systems for 2012 NIST speaker recognition evaluation,'' Proc. NIST SRE Workshop, December 2012. \\
	
	Chunlei Zhang, Fahimeh Bahmaninezhad, Shivesh Ranjan, Chengzhu Yu, {\bf Navid Shokouhi}, John H. L. Hansen. ``UTD-CRSS Systems for 2016 NIST Speaker Recognition Evaluation, '' arXiv preprint arXiv:1610.07651, October 2016. 
	
